Type Error Telemetry at Scale

### 2023-09-24 programming23/paper.tex
fix a mode-upgrades todo

Similarly, mode downgrades have only a small negative effect on the
number of errors (mean -0.3, stddev 4, median 0, max -48).
%% curious outlier: downgrade added 30 errors!
Creators apparently tend switch modes only when the code is already
well typed, or close to it.\todo{What incentive is there to do so?}

@@

\section{Conclusion}
\label{s:conclusion}

>>>>

In the other direction, mode downgrades have only a small negative effect on the
number of errors (mean -0.3, stddev 4, median 0, max -48).
%% curious outlier: downgrade added 30 errors!
We would see a much larger effect here if creators used downgrades
as a quick way to silence the typechecker.
But, creators evidently switch modes only when the code is already
in well-typed shape.

@@

\section{Lessons Learned}
\label{s:conclusion}
